Positivity-Preserving Adaptive Runge--Kutta Methods

### 2020-05-11 nusslein_vsrp/latex/overview.tex
remove ECRC

\title{Positivity-Preserving Adaptive Runge--Kutta Methods}
\author[1]{Stephan Nüßlein\thanks{\orcid{0000-0002-2455-4222}}}
\author[1]{Hendrik Ranocha\thanks{\orcid{0000-0002-3456-2277}}}
\author[1]{David I. Ketcheson\thanks{\orcid{0000-0002-1212-126X}}}
\affil[1]{%
King Abdullah University of Science and Technology (KAUST),
Extreme Computing Research Center (ECRC),
Computer Electrical and Mathematical Science and Engineering Division (CEMSE),
Thuwal, 23955-6900, Saudi Arabia}
% \date{May 11, 2020} %TODO

>>>>

\title{Positivity-Preserving Adaptive Runge--Kutta Methods}
\author[1]{Stephan Nüßlein\thanks{\orcid{0000-0002-2455-4222}}}
\author[1]{Hendrik Ranocha\thanks{\orcid{0000-0002-3456-2277}}}
\author[1]{David I. Ketcheson\thanks{\orcid{0000-0002-1212-126X}}}
\affil[1]{%
King Abdullah University of Science and Technology (KAUST),
Computer Electrical and Mathematical Science and Engineering Division (CEMSE),
Thuwal, 23955-6900, Saudi Arabia}
% \date{May 11, 2020} %TODO
